Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-09-19 CCIAQVTS/CCIAQVTS.tex
more reformats

    \begin{figure}
    \begin{nscenter}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
            \label{fig:bell_structure}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{figures/causal_structures/triangle_structure}}
            \caption{The Triangle structure consisting of three observable variables $A,B,C$ and three latent variables $X, Y, Z$.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{nscenter}
    \end{figure}

@@

    \begin{gather}
    \label[ineq]{eq:web_inequality}
        I\tsb{Web} : \\\nonumber
        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/no_symwitness_ineq_print_standalone_halfed}
    \end{gather}

@@

    % \begin{figure}
    % \begin{subfigure}[b]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_2017.pdf}}
    % \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
    % \end{subfigure}
    % \begin{subfigure}[b]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_2017_lims.pdf}}
    % \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
    % \end{subfigure}
    % \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
    % \end{figure}

@@

    \begin{gather}
        \label[ineq]{eq:symmetric_web_inequality}
        I\tsb{SymmetricWeb} : \\\nonumber
        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/MosekCertFritzSym_ineq_standalone_halfed}
    \end{gather}

@@

    \begin{figure}
    \begin{nscenter}
        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_1_max_violation_2017.pdf}
        \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{Web}$. Notice that this distribution has precisely the same possibilistic structure as the Fritz distribution, as might be expected, since $I\tsb{Web}$ was specifically generated to witness the non-classicality of $\prob[\fritz]$.}
        \label{fig:maximum_violation_I_1}
    \end{nscenter}
    \end{figure}
    \begin{figure}
    \begin{nscenter}
        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_3_max_violation_2017.pdf}
        \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{SymmetricWeb}$. Notice that this distribution has precisely the same (assymetric!) possibilistic structure as the Fritz distribution, even though $I\tsb{SymmetricWeb}$ itself is symmetric with respect to permutations of the variables $A, B, C$. }
        \label{fig:maximum_violation_I_3}
    \end{nscenter}
    \end{figure}
    % \begin{figure}
    % \begin{nscenter}
    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/symmetrized_fritz.pdf}
    %         \caption{An artificially-symmetrized version of the Fritz distribution, constructed by averaging the six permutations of $\prob[\fritz]$ over the variables $A, B, C$. While this construction significantly violates $I\tsb{SymmetricWeb}$, we have no reason to believe that this distribution should actually be achievable using quantum resources in the Triangle structure, so its role here is purely apophatic.}
    %         \label{fig:symmetrized_fritz}
    % \end{nscenter}
    % \end{figure}

@@

    Our best numerical optimization of $I\tsb{Web}$ is visualized in\cref{fig:maximum_violation_I_1}. Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution; in fact \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share their \term{possibilistic structure}. A distribution's possibilistic structure is the unitization of its probabilities, i.e. the partitioning of events into disjoint subsets: one containing those events that occur with nonzero probability (possible), the other containing the zero-probability events (impossible).
    That \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} have the same possibilistic structure is not entirely unexpected;  As was mentioned in \cref{sec:found_inequalities}, as $I\tsb{Web}$ was derived specifically to prove the incompatibility of the Fritz distribution with the Triangle structure. Consequently, it seems that $I\tsb{Web}$ best witnesses incompatibility of those distributions that closely resemble the $\prob[\fritz]$. It could be, however, that the sharing of possibilistic structure is an artifact of unreliable convergence, such that the true optimally-violating $I\tsb{Web}$ quantum distribution might have a different structure.

>>>>

    \begin{figure}
    \begin{nscenter}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{figures/causal_structures/bell_structure}}
            \caption{The Bell structure consisting of two observers $A, B$ together with measurement settings $S_{A}$ and $S_{B}$ respectively. The shared latent variable is labeled $\la$.}
            \label{fig:bell_structure}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{figures/causal_structures/triangle_structure}}
            \caption{The Triangle structure consisting of three observable variables $A,B,C$ and three latent variables $X, Y, Z$.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{nscenter}
    \end{figure}

@@

    \begin{gather}
    \label[ineq]{eq:web_inequality}
        I\tsb{Web} : \\\nonumber
        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/web_ineq_standalone_halfed}
    \end{gather}

@@

    % \begin{figure}
    % \begin{subfigure}[b]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise.pdf}}
    % \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
    % \end{subfigure}
    % \begin{subfigure}[b]{.48\linewidth}
    % {\centering\includegraphics[width=\linewidth]{figures/noise/noise_lims.pdf}}
    % \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
    % \end{subfigure}
    % \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
    % \end{figure}

@@

    \begin{gather}
        \label[ineq]{eq:symmetric_web_inequality}
        I\tsb{SymmetricWeb} : \\\nonumber
        \includegraphics[clip, trim=0cm 0cm 0cm 0.5cm, width=\linewidth]{figures/inequalities/sym_web_ineq_standalone_halfed}
    \end{gather}

@@

    \begin{figure}
    \begin{nscenter}
        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_1_max_violation.pdf}
        \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{Web}$. Notice that this distribution has precisely the same possibilistic structure as the Fritz distribution, as might be expected, since $I\tsb{Web}$ was specifically generated to witness the non-classicality of $\prob[\fritz]$.}
        \label{fig:maximum_violation_I_1}
    \end{nscenter}
    \end{figure}
    \begin{figure}
    \begin{nscenter}
        \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/plotted_dist_I_3_max_violation.pdf}
        \caption{A quantum probability distribution of the Triangle structure that maximizes violation of $I\tsb{SymmetricWeb}$. Notice that this distribution has precisely the same (assymetric!) possibilistic structure as the Fritz distribution, even though $I\tsb{SymmetricWeb}$ itself is symmetric with respect to permutations of the variables $A, B, C$. }
        \label{fig:maximum_violation_I_3}
    \end{nscenter}
    \end{figure}
    % \begin{figure}
    % \begin{nscenter}
    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{figures/distributions/symmetrized_fritz.pdf}
    %         \caption{An artificially-symmetrized version of the Fritz distribution, constructed by averaging the six permutations of $\prob[\fritz]$ over the variables $A, B, C$. While this construction significantly violates $I\tsb{SymmetricWeb}$, we have no reason to believe that this distribution should actually be achievable using quantum resources in the Triangle structure, so its role here is purely apophatic.}
    %         \label{fig:symmetrized_fritz}
    % \end{nscenter}
    % \end{figure}

@@

    Our best numerical optimization of $I\tsb{Web}$ is visualized in \cref{fig:maximum_violation_I_1}. Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution; in fact \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share their \term{possibilistic structure}. A distribution's possibilistic structure is the unitization of its probabilities, i.e. the partitioning of events into disjoint subsets: one containing those events that occur with nonzero probability (possible), the other containing the zero-probability events (impossible).
    That \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} have the same possibilistic structure is not entirely unexpected;  As was mentioned in \cref{sec:found_inequalities}, as $I\tsb{Web}$ was derived specifically to prove the incompatibility of the Fritz distribution with the Triangle structure. Consequently, it seems that $I\tsb{Web}$ best witnesses incompatibility of those distributions that closely resemble the $\prob[\fritz]$. It could be, however, that the sharing of possibilistic structure is an artifact of unreliable convergence, such that the true optimally-violating $I\tsb{Web}$ quantum distribution might have a different structure.
